Pyrovelocity Notebook Usage Example

### 2024-03-26 nbs/templates/user_example/user_example.qmd
fix(nbs): use gdrive notebook in colab link Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

<a target="_blank" href="https://colab.research.google.com/github/pinellolab/pyrovelocity/blob/530-nbwf/scripts/notebooks/user_example.ipynb">
  <img 
    src="https://colab.research.google.com/assets/colab-badge.svg" 
    alt="Open In Colab"
    width="109" height="20"/>
</a> <a target="_blank" href="https://nbviewer.jupyter.org/github/pinellolab/pyrovelocity/blob/530-nbwf/scripts/notebooks/user_example.ipynb">
  <img 
    src="https://raw.githubusercontent.com/jupyter/design/master/logos/Badges/nbviewer_badge.png"
    alt="Render with nbviewer" 
    width="109" height="20"/>
</a>

>>>>

<a target="_blank" href="https://colab.research.google.com/drive/1uWTZgL5lURxoXWPjtT9IJBIJyGVVDiPg">
  <img 
    src="https://colab.research.google.com/assets/colab-badge.svg" 
    alt="Open In Colab"
    width="109" height="20"/>
</a>
